Identifying Inter-Genomic Repeats Using Fast, Approximate Methods for Betweenness Centrality

### 2015-05-07 manuscript/manuscript.tex
Added sampled paths plot.
IQR added in cutoff

% a short form should be given in case it is too long for the running head
\titlerunning{Identifying Inter-Genomic Repeats Using Fast, Approximate Betweenness Centrality}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Jay Ghurye%
\and Christopher M. Hill\and Mihai Pop}
%
\authorrunning{Identifiyng Inter-Genomic Repeats Using Fast,
Approximate Methods for Betweenness Centrality}
% (feature abused for this document to repeat the title also on left hand pages)

@@

\subsection*{Networkit}
We investigated the performance of approximate betweenness centrality algorithms on the metagenomic graphs to find inter-genome repeats. We used the implementations provided by  Networkit\cite{networkit} library. NetworKit an open source library for high-performance network analysis. It implements effecient graph algorithms and parallelize most of them. It provides implementation for variety of centrality measures. We used the implementation of approximate network centrality. NetworKit provides a parallel implementation of the algorithm by Matteo et al.\cite{matteo} which is based on sampling shortest paths. It also provides implementation for the algorithm by Geisberger et al.\cite{sanders}. However, this algorithm is not parallelized.

\begin{itemize}
\item \textbf{Scalability}: How these algorithms scale on large metagenomic repeats graph? Does parallelized algorithm provides quick results or taking sample of fewer nodes provides quick results?
\item \textbf{Accuracy}: Which of these algorithms provides better accuracy while determining inter-genomic repeats?
\item \textbf{Sample Size}: For the algorithm by Geisberger et al. \cite{sanders}, how should a sample size be defined so that accuray of repeat detection is maximized. We also stuy the effect of sample size in ghe algorithm by Matteo et al.\cite{matteo}
\end{itemize}

@@

@@

>>>>

% a short form should be given in case it is too long for the running head
\titlerunning{Inter-Genomic Repeats Using Betweenness Centrality}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Jay Ghurye%
\and Christopher M. Hill\and Mihai Pop}
%
\authorrunning{Ghurye et al.}
% (feature abused for this document to repeat the title also on left hand pages)

@@

\subsection*{Networkit}
We investigated the performance of approximate betweenness centrality algorithms on the metagenomic graphs to find inter-genome repeats. We used the implementations provided by  Networkit\cite{networkit} library. NetworKit is an open source library for high-performance network analysis. It implements effecient graph algorithms and parallelize most of them. It provides implementation for variety of centrality measures. We used the implementation of approximate betweenness centrality. NetworKit provides parallelized implementation of the algorithm by Matteo et al.\cite{matteo} which is based on sampling shortest paths. It also provides implementation for the algorithm by Geisberger et al.\cite{sanders}. However, this algorithm is not parallelized.

@@

Another cutoff criteria we test is based on \textit{interquartile range(IQR)}. Let $Q_{1}$,$Q_{2}$, and $Q_{3}$ denote lower, midle and upper quartile respectiely. IQR can be defined as the difference between the upper and lower quartile. So, $IQR = Q_{3} - Q_{1}$. For the values of centrality, we calculate upper quartile, middle quartile, lower quartile and IQR. For filtering, we mark all the nodes with centrality more than $Q_{2} + 1.5*IQR$ as repeats. The advantage of this method is that it does not make any assumptions about the distribution of underlying data.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width = \textwidth]{sampled_paths}
\caption{Example of conversion of de Bruijn graph to Repeats graph}
\label{fig:sampled_nodes}
\end{figure}
